---
title: "Do bulk-billing General Practitioner clinics provide lower quality care?"
subtitle: "Evidence from July 2024 to June 2025 data"
date: 27 February 2026
date-format: long
author: Dr David P.S. Fong
abstract: |
  General practices that predominantly bulk-bill (80% or more of consultations) perform at
  broadly similar levels to other practices across Australia's ten chronic disease Quality
  Improvement Measures (QIMs). Medians are nearly identical and performance distributions
  overlap closely across most QIMs and geographic areas.
  
  Where differences exist, they follow a consistent pattern: bulk-billing practices
  perform better on brief, non-invasive measures such as recording smoking status, alcohol
  history and weight. Bulk-billing practices perform comparatively worse on measures
  requiring more clinician time or procedures -- such as measuring glycaemic control
  in diabetes, influenza immunisation and cervical screening, particularly practices in
  urban (Modified Monash Model 1) and very remote (Modified Monash Model 6) areas.
  Structural factors, including time pressure, patients living with low socioeconomic
  resources, multiple morbidity, cultural distance and scarcity of same-gendered clinicians
  are plausible explanations for bulk-billing practices performing comparatively worse
  on some QIM measures. 

  Contrary to expectations, practices in primary health networks with lower socioeconomic
  populations -- including North West Melbourne and Western Sydney -- outperform those in
  advantaged primary health networks in the same cities. The reasons are unclear and
  warrant further investigation.
  
  Targeted support for time-intensive chronic diseases at practices with high-need and
  disadvantaged populations represent the clearest policy opportunity identified
  by this data.
number-sections: true
format: 
  html:
    toc: true
    toc-location: right
    code-fold: true
    code-summary: "Show the code"
    output: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    fontsize: 12pt
    toc: true
    output: true
    echo: false
    geometry:
      - left=20mm
      - right=20mm
      - top=20mm
      - bottom=25mm
      - textwidth=170mm
    include-in-header:
      text: |
        \usepackage{float}
        \floatplacement{figure}{H}
        \usepackage{libertinus}
execute:
  warning: false
  error: false
  message: false
  editor_options: 
  chunk_output_type: console
---

{{< pagebreak >}}

## Introduction

The universal health insurance system of Australia (Medicare) provides rebates (payments) for private health care services provided by clinicians to patients. *Bulk-billing* -- where the clinician agrees to charge the patient no more than the government-set insurance price for the service -- essentially allows the patient consultation to be 'free' (i.e. no out-of-pocket expense). The alternative to bulk-billing is that the clinician charges the patient a price greater than the government-set insurance price.

Bulk-billed services are politically popular and several recent government funding initiatives have aimed to promote and increase bulk-billing[^duckett]. The low cost of bulk-billed services (i.e. no co-payment) improves healthcare access and continuity of care for patients with low income and multiple chronic conditions[^breadon] [^butler].

[^duckett]: "Labor and the Coalition have pledged to raise GP bulk billing. Here’s what the Medicare boost means for patients", Duckett, 2025. *The Conversation*, February 23, 2025. https://theconversation.com/labor-and-the-coalition-have-pledged-to-raise-gp-bulk-billing-heres-what-the-medicare-boost-means-for-patients-250604

[^breadon]: "A new Medicare: Strengthening general practice", Breadon et al, 2022. Grattan Institute.

[^butler]: "Association of individual-socioeconomic variation in quality-of-primary care with area-level service organisation: A multilevel analysis using linked data", Butler et al, 2023. *Journal of Evaluation in Clinical Practice* **29**(6):984--997. https://doi.org/10.1111/jep.13834

Although there is no current evidence that bulk-billed services are associated with low value care such as unnecessary antibiotics and imaging[^scott], there is concern that widespread bulk-billing entrenches a dysfunctional funding model[^breadon2025]. The current Medicare rebate structure financially rewards the clinician to see a high volume of patients with many short visits rather than longer visits, regardless of the patient's needs. Shorter consultations could result in less time to explore complex or chronic conditions, less opportunity for preventive health discussions, less time to build a doctor-patient relationship and perhaps a risk of addressing only the presenting complaint rather than the 'whole patient'.

[^scott]: "Physician Competition and Low-Value Health Care", Scott et al, 2022. *American Journal of Health Economics* **8**(2):Spring 2022. https://doi.org/10.1086/718509

[^breadon2025]: "Bulk-billing rates are up. But there’s more to delivering the best possible care", Breadon and Chapman, 2025. *The Conversation*, February 13, 2026. https://theconversation.com/bulk-billing-rates-are-up-but-theres-more-to-delivering-the-best-possible-care-275669

Measurement of clinician and clinic participation in preventive health and chronic disease management activities are included in the national Quality Improvement Measures (QIMs)[^aihw_qim]. The Quality Improvement Measures (QIMs) are intended to support a regional and national understanding of chronic disease management. Quality Improvement measure include preventive vaccination for the elderly and those with chronic conditions (QIM 4, 5, 6), preventive cancer screening (QIM 9), cardiovascular risk screening (QIM 8), weight screening (QIM 3), drug and alcohol screening (QIM 2, 7) and chronic disease management and monitoring (QIM 1, 10),

[^aihw_qim]: "[Practice Incentives Program Quality Improvement Measures: annual data update 2024-2025](https://www.aihw.gov.au/reports/primary-health-care/pipqi-measures-2024-25/contents/introduction)", Australian Institute of Health and Welfare (AIHW), Australian Government

General practices receive payments to report their Quality Improvement Measures to the Primary Health Networks, but currently receive no payment for improving their scores. Primary Health Networks *do* report to participating general practices their Quality Improvement Measures scores relative to the other general practices within the same Primary Health Network.

This paper compares Quality Improvement Measure (QIM) outcomes between practices which predominantly bulk-bill 80% or more of services/consultations ('bulk-billing' practices) and other 'mixed-billing' practices during the time period July 2024 to June 2025.

*This paper is a secondary use of de-identified, aggregated practice statistics retrieved from Cubiko[^cubiko] Touchstone software, extracted February 2026. The findings in this paper are an observational, visual exploration of summary statistics. Raw data was not available for formal statistical analysis.*

*The summary statistics used was accessed from the Cubiko Insights software interface. As of 2025, Cubiko Touchstone draws upon data from 1048 Australian general practices[^hotn2025] which have opted-in to provide data for Cubiko Touchstone. The primary use of Cubiko Touchstone statistics is for internal business purposes by practices subscribing to the Cubiko Insights product. This paper has not been written or endorsed by Cubiko. The observations and commentary are of the author alone and do not represent the views or opinions of Cubiko or its employees.*

[^cubiko]: "2023 Touchstone General Practice Industry Report" (published 2024), [Cubiko](https://www.cubiko.com.au/). At the time of the 2023 report, 24% of practices contributing to Cubiko Touchstone data were predominantly bulk-billing practices (billing 80+% of consultations), 75% of practices were 'mixed billing'. The "Health of the Nation 2025" report by the RACGP notes that the bulk-billing rate remained relatively steady in the Touchstone dataset throughout 2023 and 2024.

[^hotn2025]: "Health of the Nation 2025", Royal Australian College of General Practitioners (RACGP), 2025.

## Results and Discussion

### Quality Improvement Measure performance is similar between bulk-billing clinics and mixed-billing clinics

Quality Improvement Measure (QIM) performance for bulk-billing clinics is broadly similar to mixed-billing clinics. Bulk-billing and mixed-billing clinics perform at similar levels across nearly all quality measures. The overlap in performance is substantial and the median scores nearly identical. This is the case both overall (@fig-mmm-all-qim-mean) and for most individual QIMs (@fig-mmm-all-qim-all).

For example, the top 10th centile of predominantly bulk-billling clinics perform better than the 25th centile of mixed-billing clinics, the top 25th centile of bulk-billing clinics perform better than the 50th centile (median) of mixed-billing clinics etc., and vice versa.

The statistics for a set of more homogeneous practices, such as practices located in [Modified Monash Model](https://www.health.gov.au/topics/rural-health-workforce/classifications/mmm) Area 1 (metropolitan areas of major cities) are also broadly similar for bulk-billing clinics and mixed-billing clinics (@fig-mmm-1-qim-all, @fig-mmm-all-qim-mean-comparison, @fig-mmm-all-qim-weighted-mean-comparison).

### Characteristics of Quality Improvement Measures where bulk-billing clinics tend to perform better -- or worse -- than mixed-billing clinics {#sec-individual-qim-bb-vs-mixed}

Bulk-billing clinics tend to perform better than mixed-billing clinics at quality improvement measures which involve brief and non-invasive screening and measurement (@fig-mmm-all-qim-all).

Bulk-billing clinics -- particularly in urban or very remote areas (@fig-mmm-1-qim-all, @fig-mmm-6-qim-all) -- perform comparatively worse than mixed-billing clinics at quality improvement measures requiring more patient time or discussion or persuasion, are more invasive procedures and/or more time consuming for the clinician. Bulk-billing clinics in some regional areas, e.g. MMM 4, perform relatively well in the more time-intensive QIMs (see @sec-rurality).

QIMs which involve relatively brief and non-invasive activities include smoking history (QIM 2), alcohol history (QIM 7), weight and height measurement (QIM 3) and measuring the blood pressure of those who live with diabetes (QIM 10).

More invasive and time-consuming -- for patient and/or clinician -- QIMs include blood-tests to measure glycaemic control in diabetics (QIM 1) and taking measurements -- including blood cholesterol etc.\ -- for cardiovascular risk assessment (QIM 8). The use of injectable therapeutics such as influenza vaccination (QIMs 4, 5 and 6) are both time consuming and invasive. Cervical screening (QIM 9) is even more time consuming and invasive. 

Structural factors -- not clinic quality -- likely explain why bulk-billing clinic underperform on some time-intensive QIMs. Low patient resources and cultural or social distance can reduce the effectiveness and increase the time required to discuss and carry out quality improvement activities[^valentin] [^alkhamees]. Relatively poor remuneration (if predominantly bulk-billing) and high levels of multiple morbidity[^watt] and subsequent high clinician workload[^BuffelduVaure] might restrict clinician time. Time pressures reduce health care screening activities and chronic disease management activities[^paul].

[^valentin]: "Bridging inequity gaps in healthcare through tailored support: implementation perspectives of the Social Health Bridge-Building Programme", Valentin et al, 2025 Feb. *BMC Health Services Research* **25**:208. https://doi.org/10.1186/s12913-025-12359-8

[^alkhamees]: "Patient-physician communication in intercultural settings: An integrative review", Alkhamees and Alasqah, 2023. *Heliyon* **9**(12): e2267. https://doi.org/10.1016/j.heliyon.2023.e22667

[^watt]: "General Practitioners at the Deep End: The experience and views of general practitioners working in the most severely deprived areas of Scotland", Watt et al, 2012. Occasional paper *Royal College of General Practitioners*, 2012(April) (89), i--40.

[^BuffelduVaure]: "Potential workload in applying clinical practice guidelines for patients with chronic conditions and multimorbidity: a systematic analysis" Buffel du Vaure et al, 2016. *BMJ Open* 2016;**6**:e010119. doi: 10.1136/bmjopen-2015-010119

[^paul]: "Access to chronic disease care in general practice: the acceptability of implementing systematic waiting-room screening using computer-based patient-reported risk status.", Paul et al, 2013. *The British journal of general practice : the journal of the Royal College of General Practitioners*, **63**(614), e620--e626. https://doi.org/10.3399/bjgp13X671605

Influenza vaccination rates also varies with socioeconomic status. Cultural, linguistic and socioeconomic characteristics -- including education and income -- strongly influence influenza vaccination uptake among schoolchildren[^le]. Bulk-billing rates are higher in regions with the most socioeconomically disadvantaged quintile [^saxby].

[^le]: "Socio-economic inequality underpins inequity in influenza vaccination uptake between public and private secondary schools: an Australian population-based study", Le et al, 2025. *The Lancet Regional Health. Western Pacific* **65**, 101761. https://doi.org/10.1016/j.lanwpc.2025.101761

[^saxby]: "Bulk-billing rates and out-of-pocket costs for general practitioner services in Australia, 2022, by SA3 region: analysis of Medicare claims data", Saxby and Zhang, 2024. *Medical Journal of Australia* **222**(3):144--148

Influenza vaccination rates in a clinic is improved by expenditure of clinic time and resources e.g. sending out targeted patient reminders (and using resources to plan to do so), employment of a clinic nurse and clinic nurse time to review eligible patient population in the daily appointment book.

Cervical screening in a clinic is also improved by use of clinic time and resources by planning for and sending out targeted reminders. Participation in cervical screening decreases with increasing socioeconomic disadvantage[^aihw_cst]. Additionally, cervical screening is a 'gendered' intervention. Patients of male doctors have lower cervical screening rates[^haas] [^incecushman]. Male doctors are more likely to bulk-bill[^ochre]. The lower performance of bulk-billing clinics in cervical screening could be the result of an intersection between gender, billing incentives and workforce composition.

[^aihw_cst]: "National Cervical Screening Program monitoring report 2025", *Australian Institute of Health and Welfare (AIHW)*, Australian Government, 2025, accessed 24 February 2026. https://www.aihw.gov.au/reports/cancer-screening/ncsp-monitoring-report-2025/

[^haas]: "Patient, provider, and clinic factors associated with the use of cervical cancer screening", Haas et al. *Preventive Medicine Reports* 2021 September **23**:101468. https://doi.org/10.1016/j.pmedr.2021.101468

[^incecushman]: "Association of primary care physician sex with cervical cancer and mammography screening", Ince-Cushman et al. 2013 Jan *Canadian Family Physician*  **59**(1):e11-18. https://pubmed.ncbi.nlm.nih.gov/23341674/

[^ochre]: "[Insights into gender paygap amongst General Practitioners in Australia: An Ochre Health Study](https://ochrehealth.com.au/wp-content/uploads/2025/11/Paper-Insights-into-gender-paygap-amongst-general-pracitioners-An-Ochre-Health-study-May-2025.pdf)", Ochre Health Pty Ltd., April 2025.  

Dedicated funding for practice nurse time, targeted patient recall systems, and chronic disease care coordinators at predominantly bulk-billing practices working with low resource populations could address the structural barriers of high workload, cultural distance, multiple morbidity and limited consultation time contributing to reduced performance in quality improvement measures which require additional time and discussion. Dedicated time for quality improvement from empowered clinicians is important for effective participation, planning and conduct of quality improvement activities[^Deilkås].

[^Deilkås]: "Physician participation in quality improvement work - interest and opportunity: a cross-sectional survey", Deilkås et al, 2022. *BMC primary care*, **23**(1), 267. https://doi.org/10.1186/s12875-022-01878-6

Workforce data on GP gender distribution by socioeconomic region and billing type would help clarify whether this explains the relatively poor cervical screening performance of bulk-billing clinics. Targeted incentives for female clinicians in predominantly bulk-billing settings could close the inequity.

### Rurality (Modified Monash Model areas) and Quality Improvement Measures {#sec-rurality}

The Modified Monash Model (MMM) defines whether a location is metropolitan, rural, remote or very remote[^mmm]. The MMM has been designed to designate areas of increasing disadvantage due to poor access to healthcare and increased healthcare needs, e.g. related with low socioeconomic status[^mcgrail] [^versace]. The Modified Monash Model categories (@tbl-mmm) are used to determine eligibility for health workforce programs, including increasing bulk-billing incentives[^gphotn2024] with increasing rurality.

[^mcgrail]: "Discussion Paper: Development of a national Index of Access for Primary Health Care in Australia", McGrail and Humphreys, 2015. *Centre of Research Excellence in Rural and Remote Primary Health Care*. Monash University, School of Rural Health.

[^versace]: "National analysis of the Modified Monash Model, population distribution and a socio-economic index to inform rural health workforce planning.", Versace et al, 2021. *Aust J Rural Health* 2021 Oct;**29**(5):801-810. doi: 10.1111/ajr.12805. PMID: 34672057.

[^gphotn2024]: "General Practice Health of the Nation 2024", Royal Australian College of General Practitioners, 2024.

Despite the reduced socioeconomic, education and healthcare resources available to those living in more remote areas and higher levels of morbidity, disease burden and disability [^aihw_rural_remote], the median QIM performance appears to *increase* for bulk-billing practices in MMM 4 (medium rural towns) compared to MMM 1 (metropolitan areas). @fig-mmm-all-qim-mean-comparison compares MMMs Australia-wide. @fig-phn-hneccphn-mmm-123-qim-weighted-mean-comparison compares MMMs within the Hunter New England and Central Coast PHN. MMM 5/6 QIM performance for bulk-billing practices is less than MMM 4 QIM performance, both Australia-wide and also within the HNECCPHN. @fig-mmm-4-qim-all (MMM 4) and @fig-phn-hneccphn-mmm-123-qim-weighted-mean-comparison (HNECCPHN) show the performance between bulk-billing and mixed-billing clinics for individual QIMs. In contrast to MMM 1 practices (@fig-mmm-1-qim-all), bulk-billing practices in MMM 4 perform relatively well for the time intensive QIMs (see @sec-individual-qim-bb-vs-mixed): cervical screening (QIM 9), measuring CVD risk factors (QIM 8) and influenza immunisation of at-risk populations (QIM 4, 5, 6).

[^aihw_rural_remote]: "Rural and remote health", Web article, Australian Institute of Health and Welfare (AIHW), Australian Government. retrieved March 2026. https://www.aihw.gov.au/reports/rural-remote-australians/rural-and-remote-health

These statistics are consistent with findings that cancer screening participation is sometimes highest in regional areas, rather than city areas or remote areas. Bowel cancer screening participations rates are higher for people living in inner regional areas compared to major cities or remote areas[^aihw_bowel_cancer] and breast cancer screening participation rates are higher in outer and inner regional areas compared to major cities or remote areas[^aihw_breast_cancer]. However, cervical screening participation rate was highest in major cities[^aihw_ncsp].

[^aihw_bowel_cancer]: "National Bowel Cancer Screening Progrma monitoring report 2025", Web report, Australian Institute of Health and Welfare (AIHW), Australian Government. retrieved March 2026. https://www.aihw.gov.au/reports/cancer-screening/nbcsp-monitoring-2025
[^aihw_breast_cancer]: "BreastScreen Australia monitoring report 2025", Web report, Australian Institute of Health and Welfare (AIHW), Australian Government, retrieved March 2026. https://www.aihw.gov.au/reports/cancer-screening/breastscreen-australia-monitoring-report-2025
[^aihw_ncsp]: "National Cervical Screening Program monitoring report 2025", Web report, Australian Institute of Health and Welfare (AIHW), Australian Government, retrieved March 2026. https://www.aihw.gov.au/reports/cancer-screening/ncsp-monitoring-report-2025

Modified Monash Category | Inclusions
---|---:
MM 1 | **Metropolitan areas**: Major cities accounting for 70% of Australia’s population. All areas categorised ASGS-RA1
MM 2 | **Regional centres**: Areas categorised ASGS-RA 2 and ASGS-RA 3 that are in, or within 20km road distance, of a town with a population greater than 50,000.
MM 3 | **Large rural towns**: Areas categorised ASGS-RA 2 and ASGS-RA 3 that are not in MM 2 and are in, or within 15km road distance, of a town with a population between 15,000 and 50,000.
MM 4 | **Medium rural towns**: Areas categorised ASGS-RA 2 and ASGS-RA 3 that are not in MM 2 or MM 3 and are in, or within 10km road distance, of a town with a population between 5,000 and 15,000.
MM 5 | **Small rural towns**: All other areas in ASGS-RA 2 and 3.
MM 6 | **Remote communities**: All areas categorised ASGS-RA 4 and islands that are separated from the mainland in the ABS geography and are less than 5km offshore.
MM 7 | **Very remote communities**: All other areas that are categorised ASGS-RA 5 and populated islands separated from the mainland in the ABS geography that are more than 5km offshore.

: Modified Monash Model (MMM) categories {#tbl-mmm}

[^mmm]: "About the Modified Monash Model", Department of Health, Disability and Ageing. Australian Government. retrieved 26th February 2026. https://www.health.gov.au/topics/rural-health-workforce/classifications/mmm?language=en

The reason for the relatively better performance of more regional and remote bulk-billing practices (up to MMM 4) compared to their mixed-billing peers is not clear.

General practice doctors training in rural and remote areas learn and practice clinical and reasoning skills as the result of higher levels of exposure to a diverse range of patient complexities and medical conditions[^young]. General practice doctors training in rural and remote areas also build connections with the community they work in[^kanakis], potentially improving clinical care through a clinician having better understanding of patient context. It is possible that doctors working in rural and remote areas achieve better clinical skills and better understanding of patient context which help mitigate the health outcome disadvantages of living in more remote areas.

[^young]: "A comparative evaluation of quality and depth of learning by trainee doctors in regional, rural, and remote locations", Young et al, 2023. *BMC Medical Education*. 2023 Apr 5;**23**(1):215. doi: 10.1186/s12909-023-04175-7
[^kanakis]: "How does GP training impact rural and remote underserved communities? Exploring community and professional perceptions", Kanakis et al, 2020. *BMC Health Services Research*. 2020 Aug 31;**20**(1):812. doi: 10.1186/s12913-020-05684-7

MMM 4 practices do benefit from slightly better individual bulk-billing service incentives and other workforce incentives compared to MMM 1 practices. For example, as of February 2026 the bulk-billing incentive for a typical consultation service is \$35.30[^item_75873] in a MMM 4 practice compared to \$21.85[^item_75870] for a MMM 1 practice. In addition to fee-for-service, the government pays financial incentives to doctors working in MMM 4 worth up to \$18,000 per year[^workforce_incentives_doctor] (to doctors working in both mixed-billing or bulk-billing practices). Compared to MMM 1 practices, MMM 4 practices are also paid 20% more for various practice incentives e.g. to employ a practice nurse or pharmacist[^workforce_incentives_practice].

[^item_75873]: [Medicare Benefits Schedule item 75873](https://www9.health.gov.au/mbs/fullDisplay.cfm?type=item&qt=ItemID&q=75873)
[^item_75870]: [Medicare Beneifts Schedule item 75870](https://www9.health.gov.au/mbs/fullDisplay.cfm?type=item&qt=ItemID&q=75870)
[^workforce_incentives_doctor]: ["Workforce Incentive Program Doctor Stream Guidelines"](https://www.health.gov.au/sites/default/files/2026-02/workforce-incentive-program-guidelines-doctor-stream.pdf). Effective date: 16 February 2026, Department of Health, Disability and Ageing. Australian Government.
[^workforce_incentives_practice]: ["Incentives and support for GPs, general practices and other health professionals in MM 4 locations"](https://www.health.gov.au/sites/default/files/2026-02/incentives-and-support-for-gps-and-general-practices-in-modified-monash-4-locations_0.pdf), Department of Health Disability and Ageing. Australian Government.

A potential natural experiment exists at MMM boundaries where similar bulk-billing practices on either side of MMM boundaries face different financial and workforce incentives. Differing QIM performance across MMM boundaries is potentially attributable to the difference in those incentives.

### Relative socioeconomic disadvantage between primary health networks and Quality Improvement Measures

Within each major Australian cities, some primary health networks serve populations which are, on average, more socioeconomically advantaged or disadvantaged than other primary health networks in the same city.

Quality Improvement Measure outcomes such as cervical screening and influenza vaccination vary with socioeconomic advantage[^valenti]. It could be expected that overall QIM performance might vary between primary health networks which have populations with very different socioeconomic status.

[^valenti]: "An analysis of general practice encounters by socioeconomic disadvantage", Valenti et al, 2016. *Australian Family Physician* **45**(10):702-705. https://www.racgp.org.au/afp/2016/october/an-analysis-of-general-practice-encounters-by-soci

@sec-nwmphn-emphn compares the relatively prosperous East Melbourne PHN MMM1 area to the less prosperous North West Melbourne PHN MMM1 area. @sec-wentwest-sws-sn compares the relatively prosperous North Sydney PHN MMM1 area to the less prosperous Western Sydney PHN MMM1 area and the South West Sydney PHN MMM1+2+3[^swsphn] area. 

[^swsphn]: Not enough South West Sydney MMM1 practice data is available from Cubiko for comparison statistics. The addition of MMM 2+3 to the South West Sydney PHN statistics is of interest, but has less validity than comparing purely MMM1 areas.

Contrary to expectations, practices from NWMPHN, both bulk-billing and mixed-billing, appear to have better Quality Improvement Measure performance than their counterparts working in the generally more socioeconomically advantaged EMPHN (@fig-phn-nwmphn-emphn-mmm-1-qim-weighted-mean-comparison). Likewise, WentWest practices, both bulk-billing and mixed-billing, appear to have better Quality Improvement Measure performance than their Sydney North counterparts (@fig-phn-wentwest-swsphn-sydneynorth-qim-weighted-mean-comparison) (due to different range in MMMs, the South West Sydney and Sydney North PHN statistics are not as directly comparable).

There is no obvious explanation for the unexpected finding that practices with low-resource populations have better QIM outcomes than practices from high-resource populations.

Practices with low-resource populations might be more accustomed to encountering patients with chronic conditions and practices with high-resource populations might see more patients with minor acute conditions, e.g upper respiratory tract infections (Valenti et al, 2016). Clinicians working with more patients with multiple morbidities in rural areas might develop better clinical reasoning skills (see @sec-rurality). It is unclear from existing literature whether clinicians working with low socioeconomic populations in major urban areas develop efficiencies and skills that offset the demands of working with patients with multiple morbidity and low resources.

Perhaps significant proportions of primary care general practices in higher resource populations have 'specialised' into activities such as cosmetic medicine, and have reduced emphasis on 'basic' primary care activities such as weight measurement, taking an alcohol history and checking the blood pressure of patients living with diabetes. Perhaps practices in higher resource populations have a generally higher profit motive, which is associated with poorer quality outcomes[^brosig-koch]. It may be that PHN-level chronic disease performance may be degraded not by poverty or workload, but by market specialisation in wealthier areas. Research into practice orientation in high socioeconomic areas could consider whether current incentive structures inadvertently allow high income area practices to opt out of chronic disease care.

[^brosig-koch]: "A new look at physicians’ responses to financial incentives: Quality of care, practice characteristics, and motivations", Brosig-Koch et al, 2024. *Journal of Health Economics* **94**, March 2024, 102862. https://doi.org/10.1016/j.jhealeco.2024.102862

```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(stringr)
```

```{r}
# 1) Import (skip title line)
df <- read_excel(
  "./Quality Improvement Measures vs Billing.xlsx",
  skip = 1 # skip title row
)

# 2) Reshape: Centile values -> separate columns
df_wide <- df %>%
  # keep only the five centiles we need (defensive)
  filter(Centile %in% c(10, 25, 50, 75, 90)) %>%
  # ensure a sensible order
  mutate(Centile = factor(Centile, levels = c(10, 25, 50, 75, 90))) %>%
  # pivot to wide: one row per grouping combo, columns for each centile’s Proportion
  pivot_wider(
    id_cols = c(Billing, MMM, PHN, QIM, `QIM description`),
    names_from  = Centile,
    values_from = Proportion,
    names_glue  = "p{Centile}",               # -> p10, p25, p50, p75, p90
    values_fn   = list(Proportion = ~ mean(.x, na.rm = TRUE)), 
    # ^ if duplicates exist within a group+centile, take the mean; 
    #   replace with first(.x) or sum(.x) if preferred
    values_fill = NA_real_
  )

# Result: df_wide has columns:
# Billing, MMM, PHN, QIM, QIM description, p10, p25, p50, p75, p90
```

{{< pagebreak >}}

## Modified Monash area -- All, Primary Health networks -- all

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-mmm-all-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, 10 QIMs"
# 1) Filter to MMM = "All", PHN = "All" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "All", PHN == "All") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # spread percentiles 'wide'
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed" # title in Quarto figure caption
    subtitle = "Subset: MMM = All, PHN = All\nbox = 25th– 50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

```{r}
#| label: fig-mmm-all-qim-mean
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, Mean centiles"
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "All", PHN == "All")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill 80+% vs Mixed",
    subtitle = "Mean centiles across all 10 QIMs (MMM = All, PHN = All)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

## Modified Monash Model (MMM) area comparison

```{r}
#| label: fig-mmm-all-qim-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, MMM comparison"
# compare MMM areas
# within each MMM, compare 'BB 80+' and mixed-billing
# 1) Subset to PHN = "All", exclude MMM = "All"
df_sub <- df_wide %>%
  filter(PHN == "All", MMM != "All")

# 2) Average centiles across all QIMs within each MMM x Billing group
df_avg <- df_sub %>%
  group_by(MMM, Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Ensure MMM is ordered MMM1–MMM6
df_avg <- df_avg %>%
  mutate(MMM = factor(MMM, levels = paste0("MMM", 1:6)))

# 4) Plot: all MMMs on one row, BB 80+ and Mixed dodged within each MMM
ggplot(
  df_avg,
  aes(
    x      = MMM,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat     = "identity",
    width    = 0.45,
    alpha    = 0.9,
    position = position_dodge(width = 0.6)
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title    = "Quality Improvement Measures: Bulk-Bill 80+% vs Mixed by MMM",
    subtitle = "Mean centiles across all QIMs (PHN = All)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = "MMM",
    y        = "Proportion (%)",
    fill     = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "bottom",
    plot.subtitle    = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

```{r}
#| label: fig-mmm-all-qim-weighted-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, MMM weighted mean[^weighted_mean] comparison"
# compare MMM areas with weighted means

# three QIMS (4, 5, 6) are all influenza vaccination, given very high weighting to those statistics. It is even possible for the same vaccination in an individual to be 'counted' in all three QIMs (if the patient is a 65+ year old with diabetes and COPD)
# overall, the 'weighting' of QIMs (even if not deliberately emphasised or de-emphasised) is somewhat arbitrary since the QIM distribution doesn't necessarily reflect clinical importance

# within each MMM, compare 'BB 80+' and mixed-billing
# 1) Subset to PHN = "All", exclude MMM = "All"
df_sub <- df_wide %>%
  filter(PHN == "All", MMM != "All") %>%
  # assign 1/3 (one-third) weights to vaccination QIMs
  mutate(qim_weight = if_else(QIM %in% c(4, 5, 6), 1/3, 1))

# 2) Average centiles across all QIMs within each MMM x Billing group
df_avg <- df_sub %>%
  group_by(MMM, Billing) %>%
  summarise(
    p10 = weighted.mean(p10, w = qim_weight, na.rm = TRUE),
    p25 = weighted.mean(p25, w = qim_weight, na.rm = TRUE),
    p50 = weighted.mean(p50, w = qim_weight, na.rm = TRUE),
    p75 = weighted.mean(p75, w = qim_weight, na.rm = TRUE),
    p90 = weighted.mean(p90, w = qim_weight, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Ensure MMM is ordered MMM1–MMM6
df_avg <- df_avg %>%
  mutate(MMM = factor(MMM, levels = paste0("MMM", 1:6)))

# 4) Plot: all MMMs on one row, BB 80+ and Mixed dodged within each MMM
ggplot(
  df_avg,
  aes(
    x      = MMM,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat     = "identity",
    width    = 0.45,
    alpha    = 0.9,
    position = position_dodge(width = 0.6)
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title    = "Quality Improvement Measures: Bulk-Bill 80+% vs Mixed by MMM",
    subtitle = "Weighted mean centiles across all QIMs (PHN = All)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = "MMM",
    y        = "Proportion (%)",
    fill     = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "bottom",
    plot.subtitle    = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

[^weighted_mean]: Three QIMS (4, 5, 6) are influenza vaccination QIMs. A single patient's influenza vaccination status can be counted in all three QIMs (if the patient is a 65+ year old living with diabetes and COPD). The 'weighted' mean reduces the influence of influenza vaccination QIMs by 1/3 compared to other QIMs, thereby reducing the overall influence of influenza vaccination on the mean QIM.

### Modified Monash Area -- 1, Primary Health Network -- All

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-mmm-1-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, MMM 1"

# 1) Filter to MMM = "1", PHN = "All" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1", PHN == "All") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Subset: MMM = 1, PHN = All\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

### Modified Monash Area -- 4, Primary Health Network -- All

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-mmm-4-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, MMM 4"

# 1) Filter to MMM = "1", PHN = "All" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM4", PHN == "All") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    # subtitle = "Subset: MMM = 4, PHN = All\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

### Modified Monash Area -- 6, Primary Health Network -- All

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-mmm-6-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, MMM 6"

# 1) Filter to MMM = "1", PHN = "All" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM6", PHN == "All") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    # subtitle = "Subset: MMM = 6, PHN = All\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

## Primary Health Network -- NWMPHN, Modified Monash Area -- 1

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-mmm-1-phn-nwmphn-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, NWMPHN"
# 1) Filter to MMM = "1", PHN = "NWMPHN" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1", PHN == "NWMPHN") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Subset: MMM = 1, PHN = NWMPHN\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

```{r}
#| label: fig-mmm-1-phn-nwmphn-qim-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, NWMPHN, mean comparison"
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "MMM1", PHN == "NWMPHN")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Mean centiles across all 10 QIMs (MMM = 1, PHN = NWMPHN)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

### North West Melbourne PHN vs East Melbourne PHN {#sec-nwmphn-emphn}

```{r}
#| label: fig-phn-nwmphn-emphn-mmm-1-qim-weighted-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, NWMPHN vs EMPHN, weighted mean comparison"
# compare NWMPHN to EMPHN

# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# three QIMS (4, 5, 6) are all influenza vaccination, given very high weighting to those statistics. It is even possible for the same vaccination in an individual to be 'counted' in all three QIMs (if the patient is a 65+ year old with diabetes and COPD)
# overall, the 'weighting' of QIMs (even if not deliberately emphasised or de-emphasised) is somewhat arbitrary since the QIM distribution doesn't necessarily reflect clinical importance

# within each MMM, compare 'BB 80+' and mixed-billing
# 1) Subset to PHN = "All", exclude MMM = "All"
df_sub <- df_wide %>%
  filter(
    PHN %in% c("NWMPHN", "EMPHN"),
    MMM == "MMM1",
    Billing %in% c("BB 80+", "Mixed")
  ) %>%
  mutate(
    PHN = factor(PHN, levels = c("NWMPHN", "EMPHN")),
    Billing = factor(Billing, levels = c("BB 80+", "Mixed"))
  ) %>%
  # assign 1/3 (one-third) weights to vaccination QIMs
  mutate(qim_weight = if_else(QIM %in% c(4, 5, 6), 1/3, 1))

# 2) Average centiles across all QIMs within each MMM x Billing group
df_avg <- df_sub %>%
  group_by(PHN, Billing) %>%
  summarise(
    p10 = weighted.mean(p10, w = qim_weight, na.rm = TRUE),
    p25 = weighted.mean(p25, w = qim_weight, na.rm = TRUE),
    p50 = weighted.mean(p50, w = qim_weight, na.rm = TRUE),
    p75 = weighted.mean(p75, w = qim_weight, na.rm = TRUE),
    p90 = weighted.mean(p90, w = qim_weight, na.rm = TRUE),
    .groups = "drop"
  )

# Ensure one row per box
stopifnot(all(dplyr::count(df_avg, PHN, Billing)$n == 1))

# 3) Plot: two facets (BB 80+ | Mixed), each showing the three MMMs
ggplot(
  df_avg,
  aes(
    x      = PHN,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = PHN  # color by PHN; facets distinguish Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.6, alpha = 0.95, colour = "grey20") +
  facet_wrap(~ Billing, nrow = 1) +
  scale_fill_manual(values = c("NWMPHN" = "#4E79A7", "EMPHN" = "#F28E2B")) +
  labs(
    # title = "Quality Improvement Measures by Billing and PHN\nNWMPHN and EMPHN",
    subtitle = "Weighted mean centiles across all QIMs\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "PHN"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

```{r, fig.height=10, fig.width=6.5}
#| label: fig-phn-nwmphn-emphn-mmm-1-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, NWMPHN vs EMPHN, all QIMs"

# Compare all QIMs for two PHNs
#   NWMPHN, EMPHN
# 1) Filter to PHN, Billing, build QIM labels
df_box <- df_wide %>%
  filter(
    PHN %in% c("NWMPHN", "EMPHN"),
    Billing %in% c("BB 80+", "Mixed")
  ) %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    Billing   = factor(Billing, levels = c("BB 80+", "Mixed")),
    PHN       = factor(PHN, levels = c("NWMPHN", "EMPHN"))
  ) %>%
  # 2) Ensure exactly one row per (QIM × Billing × PHN) for identity boxplots
  group_by(QIM_label, Billing, PHN) %>%
  summarise(
    p10 = mean(as.numeric(p10), na.rm = TRUE),
    p25 = mean(as.numeric(p25), na.rm = TRUE),
    p50 = mean(as.numeric(p50), na.rm = TRUE),
    p75 = mean(as.numeric(p75), na.rm = TRUE),
    p90 = mean(as.numeric(p90), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # 3) Build a unique x for each box to avoid dodging ambiguity
  mutate(x_ib = interaction(Billing, PHN, lex.order = TRUE))

# verify uniqueness: should be 1 everywhere
stopifnot(all(dplyr::count(df_box, QIM_label, x_ib)$n == 1))

# 4) Plot: facets = QIMs; x = interaction(Billing, PHN) => two Billing groups,
#    each containing three adjacent PHN boxes
ggplot(
  df_box,
  aes(
    x      = x_ib,   # unique x per (Billing × PHN)
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = PHN
  )
) +
  geom_boxplot(
    stat   = "identity",
    width  = 0.65,
    alpha  = 0.95,
    colour = "grey20"
  ) +
  facet_wrap(~ QIM_label, ncol = 2) +  
  # Optional: show PHN in tick labels; prepend Billing for clarity
  scale_x_discrete(
    labels = function(x) {
      # Turn "BB 80+ . PHN" into "BB 80+ | PHN"
      str_replace(x, "^(BB 80\\+|Mixed)\\.(NWMPHN|EMPHN)$", "\\1 | \\2")
    }
  ) +
  scale_fill_manual(values = c(
    "NWMPHN" = "#4E79A7",
    "EMPHN" = "#F28E2B"
  )) +
  labs(
    # title    = "Quality Improvement Measures by Billing and PHN\nNWMPHN vs EMPHN",
    subtitle = "box = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = NULL,
    y        = "Proportion (%)",
    fill     = "PHN"
  ) +
  annotate("segment", x = 3.5, xend = 3.5, y = -Inf, yend = Inf, colour = "grey85") +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "top",
    strip.text       = element_text(face = "bold", size = 9),
    panel.grid.minor = element_blank(),
    axis.text.x      = element_text(size = 8, angle = 30, hjust = 1)
  )
```

## Primary Health Network -- WentWest, Modified Monash Area -- 1

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-phn-wentwest-mmm-1-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, WentWest"

# 1) Filter to MMM = "1", PHN = "WentWest" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1", PHN == "WentWest") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Subset: MMM = 1, PHN = West Sydney\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

```{r}
#| label: fig-phn-wentwest-mmm-1-qim-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, NWMPHN vs EMPHN, weighted mean comparison"

# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "MMM1", PHN == "WentWest")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Mean centiles across all 10 QIMs (MMM = 1, PHN = West Sydney)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

### WentWest vs Southwest Sydney vs Sydney North {#sec-wentwest-sws-sn}

```{r}
#| label: fig-phn-wentwest-swsphn-sydneynorth-qim-weighted-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, WentWest (MMM 1) vs SWSPHN (MMM 1, 2, 3)[^SWSPHN_MMM13] vs SydneyNorth (MMM1), weighted mean comparison"

# compare WentWest to SWSPHN and SydneyNorth
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to the three MMMs, target PHN, and the two Billing groups
df_sub <- df_wide %>%
  filter(
    PHN %in% c("WentWest", "SWSPHN", "SydneyNorth"),
    Billing %in% c("BB 80+", "Mixed")
  ) %>%
  mutate(
    PHN = factor(PHN, levels = c("WentWest", "SWSPHN", "SydneyNorth")),
    Billing = factor(Billing, levels = c("BB 80+", "Mixed"))
  ) %>%
  # assign 1/3 (one-third) weights to vaccination QIMs
  # otherwise influenza vaccination is (arguably) over-represented
  # with three out of 10 QIMs being influenza vaccination
  # and one patient's influenza vaccination status can be
  # be represented in all three QIMs
  mutate(qim_weight = if_else(QIM %in% c(4, 5, 6), 1/3, 1))

# 2) Average centiles across all QIMs within each (PHN × Billing)
df_avg <- df_sub %>%
  group_by(PHN, Billing) %>%
  summarise(
    p10 = weighted.mean(p10, w = qim_weight, na.rm = TRUE),
    p25 = weighted.mean(p25, w = qim_weight, na.rm = TRUE),
    p50 = weighted.mean(p50, w = qim_weight, na.rm = TRUE),
    p75 = weighted.mean(p75, w = qim_weight, na.rm = TRUE),
    p90 = weighted.mean(p90, w = qim_weight, na.rm = TRUE),
    .groups = "drop"
  )

# Ensure one row per box
stopifnot(all(dplyr::count(df_avg, PHN, Billing)$n == 1))

# 3) Plot: two facets (BB 80+ | Mixed), each showing the three MMMs
ggplot(
  df_avg,
  aes(
    x      = PHN,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = PHN  # color by PHN; facets distinguish Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.6, alpha = 0.95, colour = "grey20") +
  facet_wrap(~ Billing, nrow = 1) +
  scale_fill_manual(values = c("WentWest" = "#4E79A7", "SWSPHN" = "#F28E2B", "SydneyNorth" = "#59A14F")) +
  labs(
    # title = "Quality Improvement Measures by Billing and PHN\nWentWest (MMM1), SWSPHN (MMM 1 to 3) and SydneyNorth (MMM1)",
    subtitle = "Weighted mean centiles across all QIMs\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "PHN"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

[^SWSPHN_MMM13]: Not enough Cubiko data for general practices in SWSPHN MMM1 (or even MMM 1+2) to compare bulk-billing and mixed-billing practices in SWSPHN MMM1. The nature of practices in a range of MMM areas is expected to be more heterogenous than practices from a single MMM area. Comparison of statistics from MMM 1+2+3 SWSPHN practices with practices from MMM 1 practices from a different PHN should be done with caution.

```{r, fig.height=10, fig.width=6.5}
#| label: fig-phn-wentwest-swsphn-sydneynorth-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, WentWest (MMM 1) vs SWSPHN (MMM 1, 2, 3) vs SydneyNorth (MMM1), all QIMs"
# Compare all QIMs for the three PHNS
#   WentWest, SWSPHN, SydneyNorth
# 1) Filter to PHN, Billing, build QIM labels
df_box <- df_wide %>%
  filter(
    PHN %in% c("WentWest", "SWSPHN", "SydneyNorth"),
    Billing %in% c("BB 80+", "Mixed")
  ) %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    Billing   = factor(Billing, levels = c("BB 80+", "Mixed")),
    PHN       = factor(PHN, levels = c("WentWest", "SWSPHN", "SydneyNorth"))
  ) %>%
  # 2) Ensure exactly one row per (QIM × Billing × PHN) for identity boxplots
  group_by(QIM_label, Billing, PHN) %>%
  summarise(
    p10 = mean(as.numeric(p10), na.rm = TRUE),
    p25 = mean(as.numeric(p25), na.rm = TRUE),
    p50 = mean(as.numeric(p50), na.rm = TRUE),
    p75 = mean(as.numeric(p75), na.rm = TRUE),
    p90 = mean(as.numeric(p90), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # 3) Build a unique x for each box to avoid dodging ambiguity
  mutate(x_ib = interaction(Billing, PHN, lex.order = TRUE))

# verify uniqueness: should be 1 everywhere
stopifnot(all(dplyr::count(df_box, QIM_label, x_ib)$n == 1))

# 4) Plot: facets = QIMs; x = interaction(Billing, PHN) => two Billing groups,
#    each containing three adjacent PHN boxes
ggplot(
  df_box,
  aes(
    x      = x_ib,   # unique x per (Billing × PHN)
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = PHN
  )
) +
  geom_boxplot(
    stat   = "identity",
    width  = 0.65,
    alpha  = 0.95,
    colour = "grey20"
  ) +
  facet_wrap(~ QIM_label, ncol = 2) +  
  # Optional: show PHN in tick labels; prepend Billing for clarity
  scale_x_discrete(
    labels = function(x) {
      # Turn "BB 80+ . PHN" into "BB 80+ | PHN"
      str_replace(x, "^(BB 80\\+|Mixed)\\.(WentWest|SWSPHN|SydneyNorth)$", "\\1 | \\2")
    }
  ) +
  scale_fill_manual(values = c(
    "WentWest" = "#4E79A7",
    "SWSPHN" = "#F28E2B",
    "SydneyNorth" = "#59A14F"
  )) +
  labs(
    # title    = "Quality Improvement Measures by Billing and PHN\nWentWest, SWSPHN, SydneyNorth",
    subtitle = "box = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = NULL,
    y        = "Proportion (%)",
    fill     = "PHN"
  ) +
  annotate("segment", x = 3.5, xend = 3.5, y = -Inf, yend = Inf, colour = "grey85") +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "top",
    strip.text       = element_text(face = "bold", size = 9),
    panel.grid.minor = element_blank(),
    axis.text.x      = element_text(size = 8, angle = 30, hjust = 1)
  )
```

## Primary Health Network -- Tasmania, Modified Monash Area -- 1 to 3

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-phn-tasmania-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, Tasmania (MMM 1+2+3)[^Tasmania_MMM123], QIM all"
# 1) Filter to MMM = "1", PHN = "WentWest" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1to3", PHN == "Tasmania") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Subset: MMM = 1+2+3, PHN = Tasmania\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

[^Tasmania_MMM123]: Not enough Cubiko data for general practices in Tasmania MMM1 (or even MMM 1+2) to compare bulk-billing and mixed-billing practices in Tasmania MMM1. The nature of practices in a range of MMM areas is expected to be more heterogenous than practices from a single MMM area.

```{r}
#| label: fig-phn-tasmania-qim-mean
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, Tasmania (MMM 1+2+3), mean comparison"
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "MMM1to3", PHN == "Tasmania")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Mean centiles across all 10 QIMs (MMM = 1+2+3, PHN = Tasmania)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

## Primary Health Network -- Hunter, New England and Central Coast

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-phn-hneccphn-mmm-1-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, HNECCPHN (MMM 1), all QIMs"

# 1) Filter to MMM = "1", PHN = "HNECCPHN" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1", PHN == "HNECCPHN") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Subset: MMM = 1, PHN = HNECCPHN\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

```{r}
#| label: fig-phn-hneccphn-mmm-1-qim--mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, HNECCPHN (MMM 1), mean comparison"
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "MMM1", PHN == "HNECCPHN")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Mixed" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed",
    subtitle = "Mean centiles across all 10 QIMs (MMM = 1, PHN = HNECCPHN)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

### Modified Monash Area comparison within HNECCPHN

```{r, fig.width=6.5}
#| label: fig-phn-hneccphn-mmm-123-qim-weighted-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, HNECCPHN, MMM zones, weighted mean comparison"

# compare three MMM groups in HNECCPHN
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to the three MMMs, target PHN, and the two Billing groups
df_sub <- df_wide %>%
  filter(
    PHN == "HNECCPHN",
    MMM %in% c("MMM1", "MMM2to4", "MMM5"),
    Billing %in% c("BB 80+", "Mixed")
  ) %>%
  mutate(
    MMM = factor(MMM, levels = c("MMM1", "MMM2to4", "MMM5")),
    Billing = factor(Billing, levels = c("BB 80+", "Mixed"))
  ) %>%
  # assign 1/3 (one-third) weights to vaccination QIMs
  # otherwise influenza vaccination is (arguably) over-represented
  # with three out of 10 QIMs being influenza vaccination
  # and one patient's influenza vaccination status can be
  # be represented in all three QIMs
  mutate(qim_weight = if_else(QIM %in% c(4, 5, 6), 1/3, 1))

# 2) Average centiles across all QIMs within each (MMM × Billing)
df_avg <- df_sub %>%
  group_by(MMM, Billing) %>%
  summarise(
    p10 = weighted.mean(p10, w = qim_weight, na.rm = TRUE),
    p25 = weighted.mean(p25, w = qim_weight, na.rm = TRUE),
    p50 = weighted.mean(p50, w = qim_weight, na.rm = TRUE),
    p75 = weighted.mean(p75, w = qim_weight, na.rm = TRUE),
    p90 = weighted.mean(p90, w = qim_weight, na.rm = TRUE),
    .groups = "drop"
  )

# Ensure one row per box
stopifnot(all(dplyr::count(df_avg, MMM, Billing)$n == 1))

# 3) Plot: two facets (BB 80+ | Mixed), each showing the three MMMs
ggplot(
  df_avg,
  aes(
    x      = MMM,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = MMM  # color by MMM; facets distinguish Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.6, alpha = 0.95, colour = "grey20") +
  facet_wrap(~ Billing, nrow = 1) +
  scale_fill_manual(values = c("MMM1" = "#4E79A7", "MMM2to4" = "#F28E2B", "MMM5" = "#59A14F")) +
  labs(
    # title = "Quality Improvement Measures by Billing and MMM",
    subtitle = "Weighted mean centiles across all QIMs (PHN = HNECCPHN)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "MMM"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

```{r, fig.height=10, fig.width=6.5}
#| label: fig-phn-hneccphn-mmm-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Mixed, HNECCPHN, across MMM 1, 2+3+4 and 5"

# 1) Filter to PHN, Billing, and the three MMMs; build QIM labels
df_box <- df_wide %>%
  filter(
    PHN == "HNECCPHN",
    Billing %in% c("BB 80+", "Mixed"),
    MMM %in% c("MMM1", "MMM2to4", "MMM5")
  ) %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    Billing   = factor(Billing, levels = c("BB 80+", "Mixed")),
    MMM       = factor(MMM,     levels = c("MMM1", "MMM2to4", "MMM5"))
  ) %>%
  # 2) Ensure exactly one row per (QIM × Billing × MMM) for identity boxplots
  group_by(QIM_label, Billing, MMM) %>%
  summarise(
    p10 = mean(as.numeric(p10), na.rm = TRUE),
    p25 = mean(as.numeric(p25), na.rm = TRUE),
    p50 = mean(as.numeric(p50), na.rm = TRUE),
    p75 = mean(as.numeric(p75), na.rm = TRUE),
    p90 = mean(as.numeric(p90), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # 3) Build a unique x for each box to avoid dodging ambiguity
  mutate(x_ib = interaction(Billing, MMM, lex.order = TRUE))

# (Defensive) verify uniqueness: should be 1 everywhere
stopifnot(all(dplyr::count(df_box, QIM_label, x_ib)$n == 1))

# 4) Plot: facets = QIMs; x = interaction(Billing, MMM) => two Billing groups,
#    each containing three adjacent MMM boxes
ggplot(
  df_box,
  aes(
    x      = x_ib,   # unique x per (Billing × MMM)
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = MMM
  )
) +
  geom_boxplot(
    stat   = "identity",
    width  = 0.65,
    alpha  = 0.95,
    colour = "grey20"
  ) +
  facet_wrap(~ QIM_label, ncol = 2) +  
  # Optional: show MMM in tick labels; prepend Billing for clarity
  scale_x_discrete(
    labels = function(x) {
      # Turn "BB 80+ . MMM1" into "BB 80+ | MMM1"
      str_replace(x, "^(BB 80\\+|Mixed)\\.(MMM1|MMM2to4|MMM5)$", "\\1 | \\2")
    }
  ) +
  scale_fill_manual(values = c(
    "MMM1"    = "#4E79A7",
    "MMM2to4" = "#F28E2B",
    "MMM5"    = "#59A14F"
  )) +
  labs(
    title    = "Quality Improvement Measures by Billing and MMM",
    subtitle = "(PHN = HNECCPHN)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = NULL,
    y        = "Proportion (%)",
    fill     = "MMM"
  ) +
  annotate("segment", x = 3.5, xend = 3.5, y = -Inf, yend = Inf, colour = "grey85") +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "top",
    strip.text       = element_text(face = "bold", size = 9),
    panel.grid.minor = element_blank(),
    axis.text.x      = element_text(size = 8, angle = 30, hjust = 1)
  )
```
