---
title: "Quality Improvement Measures and Billing"
subtitle: "July 2024 to June 2025"
number-sections: true
format: 
  html:
    toc: true
    toc-location: right
    code-fold: true
    code-summary: "Show the code"
    output: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    toc: true
    output: true
    echo: false
    geometry:
      - left=20mm
      - right=20mm
      - top=20mm
      - bottom=25mm
      - textwidth=170mm
    include-in-header:
      text: |
        \usepackage{float}
        \floatplacement{figure}{H}
execute:
  warning: false
  error: false
  message: false
  editor_options: 
  chunk_output_type: console
---

## Introduction

Comparing Quality Improvement Measure (QIM) outcomes between practices which predominantly bulk-bill (80% or more) and 'other' practices during the time period July 2024 to June 2025.

The Quality Improvement Measures are intended to support a regional and national understanding of chronic disease management in areas of high need[^1]. Though the QIMs are not designed to assess individual general practices or general practitioner performance, general practices *are* encouraged to improve their Quality Improvement Measures relative to their peers.

[^1]: [Practice Incentives Program Quality Improvement Measures: annual data update 2024-2025, AIHW](https://www.aihw.gov.au/reports/primary-health-care/pipqi-measures-2024-25/contents/introduction)

General practices are incentivised, through Practice Incentive Program payments, to report Quality Improvement Measures to Primary Health Networks. As of 2024--2025 General practices have *not* been incentivised to meet any specified performance level in any of the Quality Improvement Measures.

Data derived from Cubiko Touchstone, February 2026[^2].

[^2]: According to the "2023 Touchstone General Practice Industry Report" (published 2024), [Cubiko](https://www.cubiko.com.au/) Touchstone used data from 811 general practices. At the time, 24% of those practices were predominantly bulk-billing practices (billing 80+% of consultations), 75% of practices were 'mixed billing'.

## Results

### Quality improvement measure performance is similar between predominantly bulk-billing clinics and 'other' clinics

Quality Improvement Measure performance for predominantly bulk-billing clinics is broadly similar to 'other' clinics which privately bill more patients. Generally, the top 10th centile of predominantly bulk-billling clinics perform better than the 25th centile of 'other' clinics, the top 25th centile of bulk-billing clinics perform better than the 50th centile (median) of 'other' etc., and vice versa. This is the case both overall (@fig-mmm-all-qim-mean) for most individual QIMs (@fig-mmm-all-qim-all). 

The statistics for a set of more homogenous practices, such as practices located in [Modified Monash Model](https://www.health.gov.au/topics/rural-health-workforce/classifications/mmm) Area 1 (metropolitan areas of major cities) are also broadly similar for predominantly bulk-billing clinics and 'other' clinics (@fig-mmm-1-qim-all, @fig-mmm-all-qim-mean-comparison, @fig-mmm-all-qim-weighted-mean-comparison).

### Characteristics of quality improvement measures where predominantly bulk-billing clinics tend to perform better (or worse) than 'other' clinics

Predominantly bulk-billing clinics tend to perform better than 'other' clinic at quality improvement measures which involve brief and non-invasive screening and measurement e.g. smoking (QIM 2) and alcohol history (QIM 7),  weight and height measurement (QIM 3) and measuring the blood pressure of those who have diabetes (QIM 10).

Predominantly bulk-billing clinics tend to perform worse than 'other' clinics at quality improvement measures requiring more patient time or discussion or persuasion, are more invasive procedures and/or more clinician time consuming.

The first few factors may be due to low patient resources, cultural or social distance. Limitations in clinician time due to relatively poor remuneration (if predominantly bulk-billing) may also play a role.

```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(stringr)
```

```{r}
# 1) Import (skip title line)
df <- read_excel(
  "./Quality Improvement Measures vs Billing.xlsx",
  skip = 1 # skip title row
)

# 2) Reshape: Centile values -> separate columns
df_wide <- df %>%
  # keep only the five centiles we need (defensive)
  filter(Centile %in% c(10, 25, 50, 75, 90)) %>%
  # ensure a sensible order
  mutate(Centile = factor(Centile, levels = c(10, 25, 50, 75, 90))) %>%
  # pivot to wide: one row per grouping combo, columns for each centile’s Proportion
  pivot_wider(
    id_cols = c(Billing, MMM, PHN, QIM, `QIM description`),
    names_from  = Centile,
    values_from = Proportion,
    names_glue  = "p{Centile}",               # -> p10, p25, p50, p75, p90
    values_fn   = list(Proportion = ~ mean(.x, na.rm = TRUE)), 
    # ^ if duplicates exist within a group+centile, take the mean; 
    #   replace with first(.x) or sum(.x) if preferred
    values_fill = NA_real_
  )

# Result: df_wide has columns:
# Billing, MMM, PHN, QIM, QIM description, p10, p25, p50, p75, p90
```

{{< pagebreak >}}

## Modified Monash area - All, Primary Health networks - all

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-mmm-all-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, 10 QIMs"
# 1) Filter to MMM = "All", PHN = "All" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "All", PHN == "All") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # spread percentiles 'wide'
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other" # title in Quarto figure caption
    subtitle = "Subset: MMM = All, PHN = All\nbox = 25th– 50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

```{r}
#| label: fig-mmm-all-qim-mean
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, Mean centiles"
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "All", PHN == "All")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill 80+% vs Other",
    subtitle = "Mean centiles across all 10 QIMs (MMM = All, PHN = All)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

## Modified Monash Area - 1, Primary Health Network - All

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-mmm-1-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, MMM 1"

# 1) Filter to MMM = "1", PHN = "All" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1", PHN == "All") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Subset: MMM = 1, PHN = All\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

### Modified Monash Model (MMM) area comparison

```{r}
#| label: fig-mmm-all-qim-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, MMM comparison"
# compare MMM areas
# within each MMM, compare 'BB 80+' and 'Other'
# 1) Subset to PHN = "All", exclude MMM = "All"
df_sub <- df_wide %>%
  filter(PHN == "All", MMM != "All")

# 2) Average centiles across all QIMs within each MMM x Billing group
df_avg <- df_sub %>%
  group_by(MMM, Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Ensure MMM is ordered MMM1–MMM6
df_avg <- df_avg %>%
  mutate(MMM = factor(MMM, levels = paste0("MMM", 1:6)))

# 4) Plot: all MMMs on one row, BB 80+ and Other dodged within each MMM
ggplot(
  df_avg,
  aes(
    x      = MMM,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat     = "identity",
    width    = 0.45,
    alpha    = 0.9,
    position = position_dodge(width = 0.6)
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title    = "Quality Improvement Measures: Bulk-Bill 80+% vs Other by MMM",
    subtitle = "Mean centiles across all QIMs (PHN = All)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = "MMM",
    y        = "Proportion (%)",
    fill     = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "bottom",
    plot.subtitle    = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

```{r}
#| label: fig-mmm-all-qim-weighted-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, MMM weighted mean[^weighted_mean] comparison"
# compare MMM areas with weighted means

# three QIMS (4, 5, 6) are all influenza vaccination, given very high weighting to those statistics. It is even possible for the same vaccination in an individual to be 'counted' in all three QIMs (if the patient is a 65+ year old with diabetes and COPD)
# overall, the 'weighting' of QIMs (even if not deliberately emphasised or de-emphasised) is somewhat arbitrary since the QIM distribution doesn't necessarily reflect clinical importance

# within each MMM, compare 'BB 80+' and 'Other'
# 1) Subset to PHN = "All", exclude MMM = "All"
df_sub <- df_wide %>%
  filter(PHN == "All", MMM != "All") %>%
  # assign 1/3 (one-third) weights to vaccination QIMs
  mutate(qim_weight = if_else(QIM %in% c(4, 5, 6), 1/3, 1))

# 2) Average centiles across all QIMs within each MMM x Billing group
df_avg <- df_sub %>%
  group_by(MMM, Billing) %>%
  summarise(
    p10 = weighted.mean(p10, w = qim_weight, na.rm = TRUE),
    p25 = weighted.mean(p25, w = qim_weight, na.rm = TRUE),
    p50 = weighted.mean(p50, w = qim_weight, na.rm = TRUE),
    p75 = weighted.mean(p75, w = qim_weight, na.rm = TRUE),
    p90 = weighted.mean(p90, w = qim_weight, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Ensure MMM is ordered MMM1–MMM6
df_avg <- df_avg %>%
  mutate(MMM = factor(MMM, levels = paste0("MMM", 1:6)))

# 4) Plot: all MMMs on one row, BB 80+ and Other dodged within each MMM
ggplot(
  df_avg,
  aes(
    x      = MMM,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat     = "identity",
    width    = 0.45,
    alpha    = 0.9,
    position = position_dodge(width = 0.6)
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title    = "Quality Improvement Measures: Bulk-Bill 80+% vs Other by MMM",
    subtitle = "Weighted mean centiles across all QIMs (PHN = All)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = "MMM",
    y        = "Proportion (%)",
    fill     = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "bottom",
    plot.subtitle    = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

[^weighted_mean]: Three QIMS (4, 5, 6) are influenza vaccination QIMs. A single patient's influenza vaccination status can be counted in all three QIMs (if the patient is a 65+ year old living with diabetes and COPD). The 'weighted' mean reduces the influence of influenza vaccination QIMs by 1/3 compared to other QIMs, thereby reducing the overall influence of influenza vaccination on the mean QIM.

## Primary Health Network - NWMPHN, Modified Monash Area - 1

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-mmm-1-phn-nwmphn-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, NWMPHN"
# 1) Filter to MMM = "1", PHN = "NWMPHN" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1", PHN == "NWMPHN") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Subset: MMM = 1, PHN = NWMPHN\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

```{r}
#| label: fig-mmm-1-phn-nwmphn-qim-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, NWMPHN, mean comparison"
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "MMM1", PHN == "NWMPHN")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Mean centiles across all 10 QIMs (MMM = 1, PHN = NWMPHN)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

### North West Melbourne PHN vs East Melbourne PHN

```{r}
#| label: fig-phn-nwmphn-emphn-mmm-1-qim-weighted-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, NWMPHN vs EMPHN, weighted mean comparison"
# compare NWMPHN to EMPHN

# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# three QIMS (4, 5, 6) are all influenza vaccination, given very high weighting to those statistics. It is even possible for the same vaccination in an individual to be 'counted' in all three QIMs (if the patient is a 65+ year old with diabetes and COPD)
# overall, the 'weighting' of QIMs (even if not deliberately emphasised or de-emphasised) is somewhat arbitrary since the QIM distribution doesn't necessarily reflect clinical importance

# within each MMM, compare 'BB 80+' and 'Other'
# 1) Subset to PHN = "All", exclude MMM = "All"
df_sub <- df_wide %>%
  filter(
    PHN %in% c("NWMPHN", "EMPHN"),
    MMM == "MMM1",
    Billing %in% c("BB 80+", "Other")
  ) %>%
  mutate(
    PHN = factor(PHN, levels = c("NWMPHN", "EMPHN")),
    Billing = factor(Billing, levels = c("BB 80+", "Other"))
  ) %>%
  # assign 1/3 (one-third) weights to vaccination QIMs
  mutate(qim_weight = if_else(QIM %in% c(4, 5, 6), 1/3, 1))

# 2) Average centiles across all QIMs within each MMM x Billing group
df_avg <- df_sub %>%
  group_by(PHN, Billing) %>%
  summarise(
    p10 = weighted.mean(p10, w = qim_weight, na.rm = TRUE),
    p25 = weighted.mean(p25, w = qim_weight, na.rm = TRUE),
    p50 = weighted.mean(p50, w = qim_weight, na.rm = TRUE),
    p75 = weighted.mean(p75, w = qim_weight, na.rm = TRUE),
    p90 = weighted.mean(p90, w = qim_weight, na.rm = TRUE),
    .groups = "drop"
  )

# Ensure one row per box
stopifnot(all(dplyr::count(df_avg, PHN, Billing)$n == 1))

# 3) Plot: two facets (BB 80+ | Other), each showing the three MMMs
ggplot(
  df_avg,
  aes(
    x      = PHN,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = PHN  # color by PHN; facets distinguish Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.6, alpha = 0.95, colour = "grey20") +
  facet_wrap(~ Billing, nrow = 1) +
  scale_fill_manual(values = c("NWMPHN" = "#4E79A7", "EMPHN" = "#F28E2B")) +
  labs(
    # title = "Quality Improvement Measures by Billing and PHN\nNWMPHN and EMPHN",
    subtitle = "Weighted mean centiles across all QIMs\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "PHN"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

```{r, fig.height=10, fig.width=6.5}
#| label: fig-phn-nwmphn-emphn-mmm-1-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, NWMPHN vs EMPHN, all QIMs"

# Compare all QIMs for two PHNs
#   NWMPHN, EMPHN
# 1) Filter to PHN, Billing, build QIM labels
df_box <- df_wide %>%
  filter(
    PHN %in% c("NWMPHN", "EMPHN"),
    Billing %in% c("BB 80+", "Other")
  ) %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    Billing   = factor(Billing, levels = c("BB 80+", "Other")),
    PHN       = factor(PHN, levels = c("NWMPHN", "EMPHN"))
  ) %>%
  # 2) Ensure exactly one row per (QIM × Billing × PHN) for identity boxplots
  group_by(QIM_label, Billing, PHN) %>%
  summarise(
    p10 = mean(as.numeric(p10), na.rm = TRUE),
    p25 = mean(as.numeric(p25), na.rm = TRUE),
    p50 = mean(as.numeric(p50), na.rm = TRUE),
    p75 = mean(as.numeric(p75), na.rm = TRUE),
    p90 = mean(as.numeric(p90), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # 3) Build a unique x for each box to avoid dodging ambiguity
  mutate(x_ib = interaction(Billing, PHN, lex.order = TRUE))

# verify uniqueness: should be 1 everywhere
stopifnot(all(dplyr::count(df_box, QIM_label, x_ib)$n == 1))

# 4) Plot: facets = QIMs; x = interaction(Billing, PHN) => two Billing groups,
#    each containing three adjacent PHN boxes
ggplot(
  df_box,
  aes(
    x      = x_ib,   # unique x per (Billing × PHN)
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = PHN
  )
) +
  geom_boxplot(
    stat   = "identity",
    width  = 0.65,
    alpha  = 0.95,
    colour = "grey20"
  ) +
  facet_wrap(~ QIM_label, ncol = 2) +  
  # Optional: show PHN in tick labels; prepend Billing for clarity
  scale_x_discrete(
    labels = function(x) {
      # Turn "BB 80+ . PHN" into "BB 80+ | PHN"
      str_replace(x, "^(BB 80\\+|Other)\\.(NWMPHN|EMPHN)$", "\\1 | \\2")
    }
  ) +
  scale_fill_manual(values = c(
    "NWMPHN" = "#4E79A7",
    "EMPHN" = "#F28E2B"
  )) +
  labs(
    # title    = "Quality Improvement Measures by Billing and PHN\nNWMPHN vs EMPHN",
    subtitle = "box = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = NULL,
    y        = "Proportion (%)",
    fill     = "PHN"
  ) +
  annotate("segment", x = 3.5, xend = 3.5, y = -Inf, yend = Inf, colour = "grey85") +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "top",
    strip.text       = element_text(face = "bold", size = 9),
    panel.grid.minor = element_blank(),
    axis.text.x      = element_text(size = 8, angle = 30, hjust = 1)
  )
```

## Primary Health Network - WentWest, Modified Monash Area - 1

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-phn-wentwest-mmm-1-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, WentWest"

# 1) Filter to MMM = "1", PHN = "WentWest" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1", PHN == "WentWest") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Subset: MMM = 1, PHN = West Sydney\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

```{r}
#| label: fig-phn-wentwest-mmm-1-qim-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, NWMPHN vs EMPHN, weighted mean comparison"

# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "MMM1", PHN == "WentWest")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Mean centiles across all 10 QIMs (MMM = 1, PHN = West Sydney)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

### WentWest vs Southwest Sydney vs Sydney North

```{r}
#| label: fig-phn-wentwest-swsphn-sydneynorth-qim-weighted-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, WentWest (MMM 1) vs SWSPHN (MMM 1, 2, 3)[^SWSPHN_MMM13] vs SydneyNorth (MMM1), weighted mean comparison"

# compare WentWest to SWSPHN and SydneyNorth
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to the three MMMs, target PHN, and the two Billing groups
df_sub <- df_wide %>%
  filter(
    PHN %in% c("WentWest", "SWSPHN", "SydneyNorth"),
    Billing %in% c("BB 80+", "Other")
  ) %>%
  mutate(
    PHN = factor(PHN, levels = c("WentWest", "SWSPHN", "SydneyNorth")),
    Billing = factor(Billing, levels = c("BB 80+", "Other"))
  ) %>%
  # assign 1/3 (one-third) weights to vaccination QIMs
  # otherwise influenza vaccination is (arguably) over-represented
  # with three out of 10 QIMs being influenza vaccination
  # and one patient's influenza vaccination status can be
  # be represented in all three QIMs
  mutate(qim_weight = if_else(QIM %in% c(4, 5, 6), 1/3, 1))

# 2) Average centiles across all QIMs within each (PHN × Billing)
df_avg <- df_sub %>%
  group_by(PHN, Billing) %>%
  summarise(
    p10 = weighted.mean(p10, w = qim_weight, na.rm = TRUE),
    p25 = weighted.mean(p25, w = qim_weight, na.rm = TRUE),
    p50 = weighted.mean(p50, w = qim_weight, na.rm = TRUE),
    p75 = weighted.mean(p75, w = qim_weight, na.rm = TRUE),
    p90 = weighted.mean(p90, w = qim_weight, na.rm = TRUE),
    .groups = "drop"
  )

# Ensure one row per box
stopifnot(all(dplyr::count(df_avg, PHN, Billing)$n == 1))

# 3) Plot: two facets (BB 80+ | Other), each showing the three MMMs
ggplot(
  df_avg,
  aes(
    x      = PHN,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = PHN  # color by PHN; facets distinguish Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.6, alpha = 0.95, colour = "grey20") +
  facet_wrap(~ Billing, nrow = 1) +
  scale_fill_manual(values = c("WentWest" = "#4E79A7", "SWSPHN" = "#F28E2B", "SydneyNorth" = "#59A14F")) +
  labs(
    # title = "Quality Improvement Measures by Billing and PHN\nWentWest (MMM1), SWSPHN (MMM 1 to 3) and SydneyNorth (MMM1)",
    subtitle = "Weighted mean centiles across all QIMs\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "PHN"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

[^SWSPHN_MMM13]: Not enough Cubiko data for general practices in SWSPHN MMM1 (or even MMM 1+2) to compare bulk-billing and 'other' billing practices in SWSPHN MMM1. The nature of practices in a range of MMM areas is expected to be more heterogenous than practices from a single MMM area. Comparison of statistics from MMM 1+2+3 SWSPHN practices with practices from MMM 1 practices from a different PHN should be done with caution.

```{r, fig.height=10, fig.width=6.5}
#| label: fig-phn-wentwest-swsphn-sydneynorth-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, WentWest (MMM 1) vs SWSPHN (MMM 1, 2, 3) vs SydneyNorth (MMM1), all QIMs"
# Compare all QIMs for the three PHNS
#   WentWest, SWSPHN, SydneyNorth
# 1) Filter to PHN, Billing, build QIM labels
df_box <- df_wide %>%
  filter(
    PHN %in% c("WentWest", "SWSPHN", "SydneyNorth"),
    Billing %in% c("BB 80+", "Other")
  ) %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    Billing   = factor(Billing, levels = c("BB 80+", "Other")),
    PHN       = factor(PHN, levels = c("WentWest", "SWSPHN", "SydneyNorth"))
  ) %>%
  # 2) Ensure exactly one row per (QIM × Billing × PHN) for identity boxplots
  group_by(QIM_label, Billing, PHN) %>%
  summarise(
    p10 = mean(as.numeric(p10), na.rm = TRUE),
    p25 = mean(as.numeric(p25), na.rm = TRUE),
    p50 = mean(as.numeric(p50), na.rm = TRUE),
    p75 = mean(as.numeric(p75), na.rm = TRUE),
    p90 = mean(as.numeric(p90), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # 3) Build a unique x for each box to avoid dodging ambiguity
  mutate(x_ib = interaction(Billing, PHN, lex.order = TRUE))

# verify uniqueness: should be 1 everywhere
stopifnot(all(dplyr::count(df_box, QIM_label, x_ib)$n == 1))

# 4) Plot: facets = QIMs; x = interaction(Billing, PHN) => two Billing groups,
#    each containing three adjacent PHN boxes
ggplot(
  df_box,
  aes(
    x      = x_ib,   # unique x per (Billing × PHN)
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = PHN
  )
) +
  geom_boxplot(
    stat   = "identity",
    width  = 0.65,
    alpha  = 0.95,
    colour = "grey20"
  ) +
  facet_wrap(~ QIM_label, ncol = 2) +  
  # Optional: show PHN in tick labels; prepend Billing for clarity
  scale_x_discrete(
    labels = function(x) {
      # Turn "BB 80+ . PHN" into "BB 80+ | PHN"
      str_replace(x, "^(BB 80\\+|Other)\\.(WentWest|SWSPHN|SydneyNorth)$", "\\1 | \\2")
    }
  ) +
  scale_fill_manual(values = c(
    "WentWest" = "#4E79A7",
    "SWSPHN" = "#F28E2B",
    "SydneyNorth" = "#59A14F"
  )) +
  labs(
    # title    = "Quality Improvement Measures by Billing and PHN\nWentWest, SWSPHN, SydneyNorth",
    subtitle = "box = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = NULL,
    y        = "Proportion (%)",
    fill     = "PHN"
  ) +
  annotate("segment", x = 3.5, xend = 3.5, y = -Inf, yend = Inf, colour = "grey85") +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "top",
    strip.text       = element_text(face = "bold", size = 9),
    panel.grid.minor = element_blank(),
    axis.text.x      = element_text(size = 8, angle = 30, hjust = 1)
  )
```

## Primary Health Network - Tasmania, Modified Monash Area - 1 to 3

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-phn-tasmania-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, Tasmania (MMM 1+2+3)[^Tasmania_MMM123], QIM all"
# 1) Filter to MMM = "1", PHN = "WentWest" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1to3", PHN == "Tasmania") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Subset: MMM = 1+2+3, PHN = Tasmania\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

[^Tasmania_MMM123]: Not enough Cubiko data for general practices in Tasmania MMM1 (or even MMM 1+2) to compare bulk-billing and 'other' billing practices in Tasmania MMM1. The nature of practices in a range of MMM areas is expected to be more heterogenous than practices from a single MMM area.

```{r}
#| label: fig-phn-tasmania-qim-mean
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, Tasmania (MMM 1+2+3), mean comparison"
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "MMM1to3", PHN == "Tasmania")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Mean centiles across all 10 QIMs (MMM = 1+2+3, PHN = Tasmania)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

## Primary Health Network - Hunter, New England and Central Coast

```{r, fig.height = 5.5, fig.width = 6.5}
#| label: fig-phn-hneccphn-mmm-1-qim-all
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, HNECCPHN (MMM 1), all QIMs"

# 1) Filter to MMM = "1", PHN = "HNECCPHN" and prepare labels
df_box <- df_wide %>%
  filter(MMM == "MMM1", PHN == "HNECCPHN") %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    # ensure centile columns are numeric
    across(c(p10, p25, p50, p75, p90), as.numeric)
  )

# 2) Plot precomputed boxplots (whiskers = 10th/90th; box = 25th–75th; line = 50th)
ggplot(
  df_box,
  aes(
    x = QIM_label,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(
    stat = "identity",
    position = position_dodge(width = 0.85),
    width = 0.65,
    alpha = 0.9
  ) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Subset: MMM = 1, PHN = HNECCPHN\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = "Quality Improvement Measure",
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 50, hjust = 1),
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )

```

```{r}
#| label: fig-phn-hneccphn-mmm-1-qim--mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, HNECCPHN (MMM 1), mean comparison"
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to MMM = "All", PHN = "All"
df_sub <- df_wide %>%
  filter(MMM == "MMM1", PHN == "HNECCPHN")

# 2) Average centiles across all QIMs within each Billing group
df_avg <- df_sub %>%
  group_by(Billing) %>%
  summarise(
    p10 = mean(p10, na.rm = TRUE),
    p25 = mean(p25, na.rm = TRUE),
    p50 = mean(p50, na.rm = TRUE),
    p75 = mean(p75, na.rm = TRUE),
    p90 = mean(p90, na.rm = TRUE),
    .groups = "drop"
  )

# 3) Plot: two precomputed (stat = "identity") boxplots, one per Billing
ggplot(
  df_avg,
  aes(
    x = Billing,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.45, alpha = 0.9) +
  scale_fill_manual(values = c("BB 80+" = "#1f77b4", "Other" = "#ff7f0e")) +
  labs(
    # title = "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other",
    subtitle = "Mean centiles across all 10 QIMs (MMM = 1, PHN = HNECCPHN)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "Billing"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

### Modified Monash Area comparison within HNECCPHN

```{r, fig.width=6.5}
#| label: fig-phn-hneccphn-mmm-123-qim-weighted-mean-comparison
#| fig-cap: "Quality Improvement Measures: Bulk-Bill (BB) 80+% vs Other, HNECCPHN, MMM zones, weighted mean comparison"
# compare three MMM groups in HNECCPHN
# df_wide columns assumed:
# Billing, MMM, PHN, QIM, `QIM description`, p10, p25, p50, p75, p90

# 1) Subset to the three MMMs, target PHN, and the two Billing groups
df_sub <- df_wide %>%
  filter(
    PHN == "HNECCPHN",
    MMM %in% c("MMM1", "MMM2to4", "MMM5"),
    Billing %in% c("BB 80+", "Other")
  ) %>%
  mutate(
    MMM = factor(MMM, levels = c("MMM1", "MMM2to4", "MMM5")),
    Billing = factor(Billing, levels = c("BB 80+", "Other"))
  ) %>%
  # assign 1/3 (one-third) weights to vaccination QIMs
  # otherwise influenza vaccination is (arguably) over-represented
  # with three out of 10 QIMs being influenza vaccination
  # and one patient's influenza vaccination status can be
  # be represented in all three QIMs
  mutate(qim_weight = if_else(QIM %in% c(4, 5, 6), 1/3, 1))

# 2) Average centiles across all QIMs within each (MMM × Billing)
df_avg <- df_sub %>%
  group_by(MMM, Billing) %>%
  summarise(
    p10 = weighted.mean(p10, w = qim_weight, na.rm = TRUE),
    p25 = weighted.mean(p25, w = qim_weight, na.rm = TRUE),
    p50 = weighted.mean(p50, w = qim_weight, na.rm = TRUE),
    p75 = weighted.mean(p75, w = qim_weight, na.rm = TRUE),
    p90 = weighted.mean(p90, w = qim_weight, na.rm = TRUE),
    .groups = "drop"
  )

# Ensure one row per box
stopifnot(all(dplyr::count(df_avg, MMM, Billing)$n == 1))

# 3) Plot: two facets (BB 80+ | Other), each showing the three MMMs
ggplot(
  df_avg,
  aes(
    x      = MMM,
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = MMM  # color by MMM; facets distinguish Billing
  )
) +
  geom_boxplot(stat = "identity", width = 0.6, alpha = 0.95, colour = "grey20") +
  facet_wrap(~ Billing, nrow = 1) +
  scale_fill_manual(values = c("MMM1" = "#4E79A7", "MMM2to4" = "#F28E2B", "MMM5" = "#59A14F")) +
  labs(
    # title = "Quality Improvement Measures by Billing and MMM",
    subtitle = "Weighted mean centiles across all QIMs (PHN = HNECCPHN)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x = NULL,
    y = "Proportion (%)",
    fill = "MMM"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    plot.subtitle = element_text(lineheight = 1.1),
    panel.grid.minor = element_blank()
  )
```

```{r, fig.height=10, fig.width=6.5}
# 1) Filter to PHN, Billing, and the three MMMs; build QIM labels
df_box <- df_wide %>%
  filter(
    PHN == "HNECCPHN",
    Billing %in% c("BB 80+", "Other"),
    MMM %in% c("MMM1", "MMM2to4", "MMM5")
  ) %>%
  mutate(
    QIM_label = paste0(QIM, ". ", `QIM description`),
    QIM_label = fct_reorder(QIM_label, QIM),
    Billing   = factor(Billing, levels = c("BB 80+", "Other")),
    MMM       = factor(MMM,     levels = c("MMM1", "MMM2to4", "MMM5"))
  ) %>%
  # 2) Ensure exactly one row per (QIM × Billing × MMM) for identity boxplots
  group_by(QIM_label, Billing, MMM) %>%
  summarise(
    p10 = mean(as.numeric(p10), na.rm = TRUE),
    p25 = mean(as.numeric(p25), na.rm = TRUE),
    p50 = mean(as.numeric(p50), na.rm = TRUE),
    p75 = mean(as.numeric(p75), na.rm = TRUE),
    p90 = mean(as.numeric(p90), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # 3) Build a unique x for each box to avoid dodging ambiguity
  mutate(x_ib = interaction(Billing, MMM, lex.order = TRUE))

# (Defensive) verify uniqueness: should be 1 everywhere
stopifnot(all(dplyr::count(df_box, QIM_label, x_ib)$n == 1))

# 4) Plot: facets = QIMs; x = interaction(Billing, MMM) => two Billing groups,
#    each containing three adjacent MMM boxes
ggplot(
  df_box,
  aes(
    x      = x_ib,   # unique x per (Billing × MMM)
    ymin   = p10,
    lower  = p25,
    middle = p50,
    upper  = p75,
    ymax   = p90,
    fill   = MMM
  )
) +
  geom_boxplot(
    stat   = "identity",
    width  = 0.65,
    alpha  = 0.95,
    colour = "grey20"
  ) +
  facet_wrap(~ QIM_label, ncol = 2) +  
  # Optional: show MMM in tick labels; prepend Billing for clarity
  scale_x_discrete(
    labels = function(x) {
      # Turn "BB 80+ . MMM1" into "BB 80+ | MMM1"
      str_replace(x, "^(BB 80\\+|Other)\\.(MMM1|MMM2to4|MMM5)$", "\\1 | \\2")
    }
  ) +
  scale_fill_manual(values = c(
    "MMM1"    = "#4E79A7",
    "MMM2to4" = "#F28E2B",
    "MMM5"    = "#59A14F"
  )) +
  labs(
    title    = "Quality Improvement Measures by Billing and MMM",
    subtitle = "(PHN = HNECCPHN)\nbox = 25th–50th–75th; whiskers = 10th/90th centiles",
    x        = NULL,
    y        = "Proportion (%)",
    fill     = "MMM"
  ) +
  annotate("segment", x = 3.5, xend = 3.5, y = -Inf, yend = Inf, colour = "grey85") +
  theme_minimal(base_size = 12) +
  theme(
    legend.position  = "top",
    strip.text       = element_text(face = "bold", size = 9),
    panel.grid.minor = element_blank(),
    axis.text.x      = element_text(size = 8, angle = 30, hjust = 1)
  )
```
